Designing Types for R, Empirically

### 2020-10-15 paper/main.tex
wip

\subsection{Synthesizing signatures}

The output of the \typetracer tool consists of a set of tuples of raw
types, each representing a function call in some program's
execution. The inference step consolidates the different tuples
corresponding to a particular function definition across multiple
programs and distills them into a single type signature.  The shape of
the inferred function signatures is:

@@

\noindent
In other words, we take the union of the types occurring at individual
argument positions rather than an union of function
types. Furthermore, we apply some transformation on the types to keep
the size of types in check.  Figure~\ref{fig:siplification-rules}
overviews the main simplification rules as well as the simple notion
of subtyping that we have adopted here.

@@

Assuming that type sequences can be reordered freely, we rewrite types
to minimize their size by removing redundant types, types that are
subsumed by subtyping, immutable lists, and remove \nul type to
replace them with nullables.  Functions are limited to twenty
arguments as a simplifying assumption. Higher-order functions are
conservatively inferred as \any $\rightarrow$ \any by \typetracer.

>>>>

\subsection{Synthesizing function type signatures}

In order to keep the type signatures compact, we will compact
union of arrows into a single top-level arrow with unions
at each argument position. Thus, the shape of function
signatures will be as follows:

@@

\noindent
In other words, we take the union of the types occurring at individual
argument positions rather than an union of function
types. Furthermore, we apply some transformation on the types to keep
the size of types in check.  Figure~\ref{fig:siplification-rules}
overviews the main simplification rules that we have adopted here.

@@

Assuming that type sequences can be reordered freely, we rewrite types
to minimize their size by removing redundant types, types that are
subsumed by subtyping, immutable lists, and remove \nul type to
replace them with nullables.  Higher-order functions are
conservatively treated as \any $\rightarrow$ \any.
